Determining the alternatives for scalar implicature

### 2016-05-10 Paper/Paper.Rmd
edits to fig 5 spacing

On each trial participants were presented with a target scalar item from five scales, selected from the entailment items used in @vantiel2014b. These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the food was \____," with a target scalar presented in the blank. Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" Participants saw each scalar item in random order. In total each participant saw ten target scalar items (each entailment pair from the five scales selected from van Tiel et al., 2014).

@@

```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.15, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgments from Experiment 3. Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Line type denotes condition, and colors indicate the particular scalar items. Each panel shows one scalar pair, with only standard entailment pairs shown here for simplicity in reporting."}
# Get zero's in data frame
baseDf <- data.frame(degree = rep(c("hi", "low", "hi1", "hi2", "low1", "low2"), 25),
                     scale = c(rep("good_excellent", 6 * 5),
                               rep("liked_loved", 6 * 5),
                               rep("memorable_unforgettable", 6 * 5),
                               rep("palatable_delicious", 6 * 5),
                               rep("some_all", 6 * 5)),
                     stars = rep(1:5, 30),
                     combine = rep(TRUE, 150))
listeners <- bind_rows(listenerE6 %>% mutate(expt = "e6"), 
                      listenerE11 %>% mutate(expt = "e11"))
listeners <- left_join(baseDf, listeners) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p),
         expt = ifelse(degree == "hi" | degree == "low", "e6", "e11"))
listeners$word <- as.factor(with(listeners, mapply(lookupScalar, degree, scale, expt)))
listeners$plotThis <- with(listeners, ifelse(scale == "some_all" &
                               (degree == "hi" | degree == "low" | degree == "hi1" | degree == "low1"),
                               TRUE, ifelse(scale != "some_all" & (
                                 degree == "hi" | degree == "low" | degree == "hi1" | degree == "hi2"),
                                 TRUE, FALSE)))
listeners$`Scalar type` <- with(listeners, ifelse(degree == "hi" | degree == "hi1", "stronger", "weaker"))
listeners$Condition <- with(listeners, ifelse(expt == "e6", "two alts", "four alts"))

# Plot pragmatic listener data here
ggplot(subset(listeners, plotThis == TRUE),
       aes(x = stars, y = listener.p, lty = `Scalar type`, col = Condition)) + 
  geom_line() + 
  facet_grid(.~ scale) + 
  # ggtitle("Pragmatic listener judgments") +
  ylab("percentage selecting") +
  xlab("star rating") +
  theme_bw() +
  scale_colour_manual(values=c("#268bd2","#859900")) + 
  theme(strip.text.x = element_text(size = 6),
        legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 8.5),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10))
```

@@

```{r fiveAltsScatter, fig.pos = "t", fig.width=3.5, fig.height=2.25, fig.cap = "Judgments for entailment items from the four alternatives condition of Experiment 3 are plotted against model predictions using the five alternatives data from Experiment 2. Colors show the star rating for individual judgments."}

>>>>

On each trial participants were presented with a target scalar item from five scales, selected from the entailment items used in @vantiel2014b. These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the food was \____," with a target scalar presented in the blank. Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" Participants saw each scalar item in random order. In total, each participant saw ten target scalar items (each entailment pair from the five scales selected from van Tiel et al., 2014).

@@

```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgments from Experiment 3. Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Line type denotes condition, and colors indicate the particular scalar items. Each panel shows one scalar pair, with only standard entailment pairs shown here for simplicity in reporting."}
# Get zero's in data frame
baseDf <- data.frame(degree = rep(c("hi", "low", "hi1", "hi2", "low1", "low2"), 25),
                     scale = c(rep("good_excellent", 6 * 5),
                               rep("liked_loved", 6 * 5),
                               rep("memorable_unforgettable", 6 * 5),
                               rep("palatable_delicious", 6 * 5),
                               rep("some_all", 6 * 5)),
                     stars = rep(1:5, 30),
                     combine = rep(TRUE, 150))
listeners <- bind_rows(listenerE6 %>% mutate(expt = "e6"), 
                      listenerE11 %>% mutate(expt = "e11"))
listeners <- left_join(baseDf, listeners) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p),
         expt = ifelse(degree == "hi" | degree == "low", "e6", "e11"))
listeners$word <- as.factor(with(listeners, mapply(lookupScalar, degree, scale, expt)))
listeners$plotThis <- with(listeners, ifelse(scale == "some_all" &
                               (degree == "hi" | degree == "low" | degree == "hi1" | degree == "low1"),
                               TRUE, ifelse(scale != "some_all" & (
                                 degree == "hi" | degree == "low" | degree == "hi1" | degree == "hi2"),
                                 TRUE, FALSE)))
listeners$`Scalar type` <- with(listeners, ifelse(degree == "hi" | degree == "hi1", "stronger", "weaker"))
listeners$Condition <- with(listeners, ifelse(expt == "e6", "two alts", "four alts"))

# Plot pragmatic listener data here
ggplot(subset(listeners, plotThis == TRUE),
       aes(x = stars, y = listener.p, lty = `Scalar type`, col = Condition)) + 
  geom_line() + 
  facet_grid(.~ scale) + 
  # ggtitle("Pragmatic listener judgments") +
  ylab("percentage selecting") +
  xlab("star rating") +
  theme_bw() +
  scale_colour_manual(values=c("#268bd2","#859900")) + 
  theme(strip.text.x = element_text(size = 6),
        legend.position = "bottom",
        legend.box = "horizontal",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 8.5),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10))
```

@@

```{r fiveAltsScatter, fig.pos = "t", fig.width=3.5, fig.height=2, fig.cap = "Judgments for entailment items from the four alternatives condition of Experiment 3 are plotted against model predictions using the five alternatives data from Experiment 2. Colors show the star rating for individual judgments."}
